The sweet spot for local polygenic adaptation: a case study motivated by stickleback

### 2018-09-07 Stickleback_Paper.tex
origin of adaptive variants

\textbf{Pending things to do?} that maybe we do, maybe not

longer genomes ($10^8$ not $10^5$ but rescaling everything accordingly)

verify that adaptation of introduced pops is due to initial diversity not subsequent migration
\jgg{one way to do this is check the mean number of samples under the introduced populations?}

@@

%%%%%%%%%%%%%%%%%
\section{Results}

% Overview
We varied the migration rate, $m$, across separate simulations
from $5 \times 10^{-5}$ to $5 \times 10^{-1}$ per individual,
i.e., between 0.01 and 100 migrants per year to and from each of the freshwater lakes.
This had a strong effect on many aspects of adaptation,
including how fast adaptation occurred in each lake,
how much alleles were shared between lakes,
and the population genetic signals left behind.
At the lowest migration rate, lakes adapted nearly independently,
while at the highest migration rate, the habitats are beginning to act like a single metapopulation
with substantial migration load.
We will now dissect what happens between these extremes.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Local Adaptation: differentiation with gene flow}

@@

%The lowest migration rate of $10^{-5}$ also has a very low false positive rate across all $F_{st}$ threshold values.
%\subsubsection*{Low Recombination Causes Clustering}

>>>>

@@

\section{Results}

We varied the migration rate, $m$, across separate simulations
from $5 \times 10^{-5}$ to $5 \times 10^{-1}$ per individual,
i.e., between 0.01 and 100 migrants per year to and from each of the freshwater lakes.
This had a strong effect on many aspects of adaptation,
including how fast adaptation occurred in each lake,
how much alleles were shared between lakes,
and the population genetic signals left behind.
At the lowest migration rate, lakes adapted nearly independently,
while at the highest migration rate, the habitats are beginning to act like a single metapopulation
with substantial migration load.
We will now dissect what happens between these extremes.

@@

\subsection*{Local Adaptation: differentiation with gene flow}

@@

%The lowest migration rate of $10^{-5}$ also has a very low false positive rate across all $F_{st}$ threshold values.
%\subsubsection*{Low Recombination Causes Clustering}
\subsubsection*{Origin of introduced freshwater adaptive alleles}
Up to this point, we have quantified rapid and parallel adaptation and found strong evidence that sharing of alleles is (more than likely?) responsible.
However at $m$ equal to $0.1$ \emph{mig/gen/lake}, in \ref{fig:MPFAI} we see sharing of alleles with between populations,
yet \emph{Time to adaptation} is still fairly slow ($\approx 2,000$ gens).
This is surprising when considering we see a similar quantity of allele sharing at  $m$ equal to $1.0$ \emph{mig/gen/lake}, 
but much more rapid adaptation ($\approx 60$ gens). 
This $30X$ speedup in \emph{time to adaptation} seems to be the result of either subsequent migration
from the marine after the point of freshwater introduction, or, the higher saturation of pre-existing freshwater adapted alleles 
in the marine at \emph{time to introduction} allowed for selection to effectively propagate the pre-existing freshwater adapted alleles.
To explore this further, we have looked at the genealogical origins using SLiM's \emph{treeSeq} (CITE thesis, treeSeq paper)
of the adaptive variants in the introduced population (p3) at \emph{time of introduction}, when the introduced population's mean phenotype
came within 0.5 of the pre-existing freshwater population's mean phenotype.
The adaptive variants in the introduced population were defined as effect mutations at higher than 0.5 frequency in the 
introduced population, and below 0.5 frequency in the marine population.
We classified the origin of each adaptive variant, (freshwater adapted allele in the introduced population) to be:
(1) pre-existing, propagating from an ancestor that was in the initial generation introduced to the new freshwater selective pressure,
(2) subsequent migration, propagating from and ancestor who was a migrant from the ocean \emph{after} introduction,
We then averaged these 3 numbers, for each variant existing in the population.
In Figure (blah), (FINISH AFTER PLOT)
